Usable Security in Virtual Power Plants

### 2018-01-17 acmart-master/draft.tex
Started SDL

\subsection{Integration into SDL}
How to assess usability in SDL?

>>>>

\subsection{Integration into Security Development Lifecycle}
An important aspect of usability engineering is that usability must be considered early on in software product development lifecycle. Usability of a product or a system can be measured after its development but cannot be integrated thereafter. To ensure the usability of product is as required, it must be considered early on. Each product has a set of target users and their preferences must be considered before product design. \\
Microsoft has developed a Security Development Lifecycle\cite{howard2006security}, which we shall use to define where and when to use the usability framework. This lifecycle was developed to produce more secure software, and is step towards security-by-design. The Security Development Lifecycle Process is divided into several stages.
